Mapping parishe emissions: Framlingham as an example

### 2021-09-14 mappingParishes.Rmd
added annual change plots

leaflet(fram_lsoa_sf_trans) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(fillOpacity = 0.2, weight = 1.5, popup = ~(paste0("LSOA Name ", LSOA11NM.x,
                      "<br> LA: " ,LA11NM)
                      ), # popups clicked
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

@@

@@

>>>>

leaflet(fram_lsoa_sf_trans) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(fillOpacity = 0.2, weight = 1.5, popup = ~(paste0("LSOA Name ", LSOA11NM.x,
                      "<br> LSOA code:: " ,LSOA11CD,
                      "<br> LA: " ,LA11NM)
                      ), # popups clicked
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

@@

```{r getAllGasFiles}
# slightly more complex - need to load all files & select LSOAs
getGasFiles <- function(files){
  dt <- data.table::data.table()
  for(f in files){
    d <- data.table::fread(f)
    message("Loading ", f)
    names(d)
    s <- strsplit(f, "_")
    suffix <- strsplit(s[[1]][3], ".", fixed = TRUE)
    year <- suffix[[1]][1]
    d[, year := year]
    # if these variable names vary by year have to set here
    d[, total_gas_kWh := `Consumption (kWh)`]

    dt <- rbind(dt,d, fill=TRUE) # prevents breakage when new var name introduced in 2016
  }

  return(dt)
}

files <- list.files(paste0(dataFolder, "beis/subnationalGas/lsoaDom"), 
                    pattern = ".gz", full.names = TRUE)

gas_allYears <- getGasFiles(files)

gas_allYears[, total_nMeters := ifelse(is.na(`Number of meters`), # must be after 2014
                                       `Number of consuming meters`, # so this is true
                                       `Number of meters`)] # pre 2015

gas_allYears[, .(nMeters = mean(`Number of meters`),
             nConsumingMeters = mean(`Number of consuming meters`),
             nAllMeters = mean(total_nMeters)), 
             keyby = .(year)]

names(gas_allYears)
gas_allYears[, LSOA11CD := `Lower Layer Super Output Area (LSOA) Code`]

```{r plotGasOverTime}

fram_gas_allYears <- gas_allYears[LSOA11CD == "E01030172" |
                        LSOA11CD == "E01030173"]

ggplot2::ggplot(fram_gas_allYears, aes(x = year, y = total_nMeters, 
                                        group = LSOA11CD,
                                        colour = LSOA11CD)) +
  geom_line() +
  geom_point() +
  labs(y = "Total number of gas meters")

ggplot2::ggplot(fram_gas_allYears, aes(x = year, y = total_gas_kWh/1000, 
                                        group = LSOA11CD,
                                        colour = LSOA11CD)) +
  geom_line() +
  geom_point() +
  labs(y = "Total residential gas (MWh)")

ggplot2::ggplot(fram_gas_allYears, aes(x = year, y = total_gas_kWh/total_nMeters, 
                                        group = LSOA11CD,
                                        colour = LSOA11CD)) +
  geom_line() +
  geom_point() +
  labs(y = "Mean residential gas kWh per meter",
       caption = "This is an indicator of increasing energy efficiency over time")
```

@@

```{r getAllElecFiles}
# slightly more complex - need to load all files & select LSOAs
getElecFiles <- function(files){
  dt <- data.table::data.table()
  for(f in files){
    d <- data.table::fread(f)
    message("Loading ", f)
    names(d)
    s <- strsplit(f, "_")
    suffix <- strsplit(s[[1]][3], ".", fixed = TRUE)
    year <- suffix[[1]][1]
    d[, year := year]
    # if these variable names vary by year have to set here
    d[, total_elec_kWh := `Total domestic electricity consumption (kWh)`]
    d[, total_nMeters := `Total number of domestic electricity meters`]
    dt <- rbind(dt,d)
  }

  return(dt)
}

files <- list.files(paste0(dataFolder, "beis/subnationalElec/lsoaDom"), 
                    pattern = ".gz", full.names = TRUE)

elec_allYears <- getElecFiles(files)
names(elec_allYears)
elec_allYears[, LSOA11CD := `Lower Layer Super Output Area (LSOA) Code`]
elec_allYears[, LSOA11NM := `Lower Layer Super Output Area (LSOA) Name`]

```{r plotElecOverTime}

fram_elec_allYears <- elec_allYears[LSOA11CD == "E01030172" |
                        LSOA11CD == "E01030173"]

ggplot2::ggplot(fram_elec_allYears, aes(x = year, y = total_nMeters, 
                                        group = LSOA11CD,
                                        colour = LSOA11CD)) +
  geom_line() +
  geom_point() +
  labs(y = "Total number of electricity meters")

ggplot2::ggplot(fram_elec_allYears, aes(x = year, y = total_elec_kWh/1000, 
                                        group = LSOA11CD,
                                        colour = LSOA11CD)) +
  geom_line() +
  geom_point() +
  labs(y = "Total residential electricity (MWh)")

ggplot2::ggplot(fram_elec_allYears, aes(x = year, y = total_elec_kWh/total_nMeters, 
                                        group = LSOA11CD,
                                        colour = LSOA11CD)) +
  geom_line() +
  geom_point() +
  labs(y = "Mean residential kWh per meter",
       caption = "This is an indicator of increasing energy efficiency over time")
```
